Measuring starspot properties by forward modeling IGRINS spectra of \name

### 2016-07-15 document/ms.tex
Text contributed by Greg Herczeg by email on Friday July 15.

The previous sections established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a cool photosphere with a hot spot.  In this section, we will demonstrate that this same model explains the broadband spectral energy distribution and flux-calibrated optical/near-IR spectra of LkCa 4.  Periodic variability in photometry and spectral indices are reproduced by modest changes in the visible fraction of the hot spot.

\subsection{Reproducing the Spectral Energy Distribution}

\subsection{Reproducing the flux-calibrated low resolution}

Figure~\ref{fig:lores}...

\subsection{TiO Variability}

The depth of TiO and other molecular bands are a common diagnostic of spectral type (and temperature) in optical spectra.  In the 12 ESPaDOnS spectra of \name\ obtained over 14 days \citep{2014MNRAS.444.3220D}, the depth of the TiO bands vary.

Each of the TiO spectral index is correlated with the other indices.  The line depths also correlate with the $V-$band magnitude, as estimated from the ASAS-SN photometry and the $V-$band photometry provided in \citep{2014MNRAS.444.3220D} that were obtained within 6 months of the ESPaDOnS observations.

Needs a lot more.

>>>>

In the previous sections we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a cool photosphere with a hot spot.  These results have testable predictions for the spectral energy distribution (SED) and rotational modulation of features of the SED.

% quantify the spot fraction versus rotation period, and then

In \S 4.1 we describe how the two components of the photosphere fit low resolution spectra and optical photometry.  The spectral features and colors should change as the spot rotates around the star, so that the visible fraction of hot and cool spot changes.  While the variability in optical brightness is well documented and motivatet this study, in \S 4.2-4.3 we convert the $V$ band brightness to a spot filling factor and then quantify spectroscopic and color variability caused by changes in the spot filling factor.

\begin{figure}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores} 
	\vspace{-100mm}
	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
	\label{fig:lores}
\end{figure}

\subsection{The Spectral Energy Distribution}

Figure~\ref{fig:lores} shows that the two-component photosphere matches flux-calibrated spectra well from $\sim 6000-2.5$ $\mu$m.  The two components have fixed temperatures of 4200 K covering 30\% of the visible surface and 3000 K covering 70\% of the visible surface area.  The flux and extinction are then scaled to match the spectrum.

The value for the extinction depends on XXX...

\subsection{Rotational modulation of the hot spot}

Since 1992 the $V$ band brightness has varied from $12.3$ to $13.2$ mag, with a typical range of $0.5$ mag in any single epoch.  In a two-temperature atmosphere, this brightness corresponds directly to a filling factor for both components.

We model the rotational modulation of LkCa 4 in different photometric bands by fixing the two temperatures to 4200 and 3000 K and setting the 70\% covering fraction of the cool component to $V_{est}=12.85$, as estimated at the time of the IGRINS spectrum.  The colors for the two components are obtained from the main sequence colors compiled by \citet{kenyon95}.  The colors from dwarfs stars should have minimal contribution from spots; measurements of pre-main sequence colors will include some unknown contribution of spots and cannot be used for this analysis.

In these simple models, the blue emission is dominated by the hotter component, while both components contribute to the red and infrared emission.   
The $0.5$ mag range in $V$-band brightness requires at least a factor of 1.6 change in the visible surface area of hot component.  Figure~\ref{fig:spotcolors} shows the

\subsection{Rotational Modulation of TiO Depth}

The depths of TiO and other molecular bands are common diagnostics of spectral type (and therefore temperature) in optical spectra \citep[e.g.][]{kirkpatrick91}.  In a 2-temperature photosphere, the depth of observed TiO bands will depend on the fractional coverage of the components.  In this subsection, we demonstrate that the TiO band depths vary with spot coverage.

\citet{donati14} spectroscopically monitored LkCa 4 with 12 spectra obtained over 14 days, covering $\sim 4$ rotation periods.  The top panel Figure~\ref{fig:tiovar} shows two of these spectra obtained at the estimated maximum and minimum optical brightness.  Small but significant changes are seen in the TiO bands.  The blue spectrum does not change.

The TiO variability is quantified through TiO indices listed in Table~\ref{tab:tiO}.  The TiO indices are also combined into a single index by calculating by 
calculating how many standard deviations each point is from the median value of the index, and then averaging the standard deviation.  Both the raw TiO 7140 index and this combined TiO index correlate strongly with the optical brightness.  In the spectral type scheme derived by \citet{herczeg14}, the change in TiO-7140 index corresponds to a range from M1.5 (3640 K) to M2.2 (3530 K).

0 New

Reply

BundleData Science (9)
